Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex
some edits to ux section

\section{UX sprint}
\label{sec:pilot}
\indent \indent This pilot was to test-drive an experiment which examines the usability of Tor as an anonymity tool
with respect to a target demographic of users known to use Tor (journalists who have reported in other
countries). We emphasized the targeting of a high-risk user group of Tor and to 
target usability changes aimed at helping those who could not afford to make mistakes. To see 
if those users had any potentially damaging misunderstandings or incomprehensions of Tor, 
we created tasks to elicit Tor's non-typical behaviors and ask our participants to
navigate through more advanced settings.

\subsection{Experiment Overview}
\indent \indent Our experiment consisted of three parts. We first prepare our participants to perform a 
cognitive walkthrough, ask our participants to perform a list of Internet browsing 
tasks while performing a cognitive walkthrough, and finish with an exit survey to collect 
additional information.

To first ensure that our users knew what a cognitive walkthrough is, we explain what a cognitive
walkthrough and give a demonstration of a cognitive walkthrough on a non-related dummy task 
(drawing a red hexagon in the computer graphics program Paint). We then ask our users to perform
an unrelated Internet-based task (finding the population of Zimbabwe) using any browser of their choice
while performing a cognitive walkthrough along the process of completing the task. We give our 
participants feedback on how to properly conduct a cognitive walkthrough~\cite{wharton1994cognitive}.
This process was also used to get users comfortable with talking our loud with the researcher and gauge 
how comfortable users were with a computer.

@@

Tasks 1--3 test how easy it was for a user to search for, download, and install Tor Browser 
correctly for use and if they understood that they had done the tasks correctly. 
Since no software is useful if the user is not able to access it, we found it valuable
to test the usability of this process.  Additionally, tasks 4--6 highlight Tor's ``irregular'' behavior 
comparatively to other web browsers. Specifically, gauge user reactions to Tor's default
privacy-preserving search engine Startpage,  longer loading times and performance for videos, 
and disappearing tabs upon starting a new identity. Lastly, we asked our users to 
interact with and describe buttons on the toolbar to gauge user comprehension of how Tor functioned.

@@

\subsection{Methodology} 
\indent \indent We recruited five journalists from Berkeley by reaching out to journalist contacts.
 We recruited five users with an average age of 28 ($\sigma = 13 $~years). Out of 
our five participants, 3 were female.

@@

\subsection{Results}
\indent \indent This experiment uncovered a powerful vector for attack, an unlikely source
of usability issues, and insight into how to better communicate to users so that they can be 
empowered to use Tor Browser and its advanced settings.

\subsubsection{How to Attack Users}
During the task completion process, we observed that all our participants are likely 
susceptible to a search engine optimization (SEO) poisoning attack. Most of our 
participants  were on autopilot to complete this standard download task and 
were also not aware of the possibility that their download may come from an 
illegitimate source. Usually, our participants picked whichever was the first search
result and believed it to be a good enough source for the download:

@@

Luckily, all of our users managed to download Tor browser from the legitimate source. However, 
upon searching through various search engines with a clear history, we found that cnet.com or techsource.com 
 appears as the first search result. Defenses against SEO optimization would be prudent to employ.

@@

When users encountered this obstacle,
they often returned to the download page, looking for hints or documentation.
The download page did not provide help for problems such as this
that are most salient immediately after downloading.
As a result, Tor has developed a step-by-step visual guide on the download page to 
help Mac OS X users to bypassing the Gatekeeper during their download.

>>>>

\section{UX sprint}
\label{sec:pilot}
\indent \indent This pilot examined the usability of Tor as an anonymity tool
with respect to journalists, a target demographic of users known to use Tor. 
We emphasized the targeting of a high-risk user group of Tor and to 
target usability changes aimed at helping those who could not afford to make mistakes. To see 
if those users had any potentially damaging misunderstandings or incomprehensions of Tor, 
we created tasks to elicit Tor's non-typical behaviors and ask our participants to
navigate through more advanced settings.

\subsection{Experiment Overview}
\indent \indent Our experiment consisted of three parts. We first prepared our participants to perform a 
cognitive walkthrough, asked our participants to perform a list of Internet browsing 
tasks while performing a cognitive walkthrough, and finished with an exit survey to collect 
demographic information.

To first ensure that our participants are able to perform a cognitive walkthrough is, we explain what a cognitive
walkthrough is and gave a demonstration of a cognitive walkthrough on a non-related dummy task 
(drawing a red hexagon in the computer graphics program Paint). We then asked our users to perform
an unrelated Internet-based task (finding the population of Zimbabwe) using any browser of their choice
while performing a cognitive walkthrough. We took this opportunity to give our 
participants feedback on how to properly conduct a cognitive walkthrough~\cite{wharton1994cognitive}.
This process was also used to get users comfortable with talking our loud with the researcher and gauge 
how comfortable users were with a computer.

@@

Tasks 1--3 tested how easy it was for a user to search for, download, and install Tor Browser 
correctly for use and if they understood that they had done the tasks correctly. 
Since no software is useful if the user is not able to access it, we found it valuable
to test the usability of this process.  Additionally, tasks 4--6 highlighted Tor's ``irregular'' behavior 
comparatively to other web browsers. Specifically, we wanted to gauge user reactions to Tor's
privacy-preserving search engine Startpage, decreased performance, 
and side effects of advanced settings (such as disappearing tabs upon starting a new identity).
 Lastly, we asked our users to 
interact with and describe buttons on the toolbar to gauge user comprehension of how Tor functioned.

@@

\subsection{Methodology} 
\indent \indent We recruited five journalists from Berkeley by reaching out to journalist contacts.
 We recruited five users with an average age of 28 ($\sigma = 13 $~years).  Out of  %?
our five participants, 3 were female.

@@

\subsection{Results}
\indent \indent This experiment uncovered a powerful vector for attack, an unlikely source
of usability issues, and how users communicated with the current interface design.

\subsubsection{How to Attack Users}
During the task completion process, we observed that all our participants are likely 
susceptible to a search engine optimization (SEO) poisoning attack during the 
Tor download process. Most of our  participants were on autopilot and 
were also not aware of the possibility that their download may come from an 
illegitimate source. Usually, our participants picked whichever was the first search
result and believed it to be a good enough source for the download:

@@

Luckily, all of our users managed to download Tor browser from the legitimate source. However, 
defenses against SEO optimization would be prudent to employ.

@@

As a result, Tor has developed a step-by-step visual guide on the download page to 
help Mac OS X users to bypassing the Gatekeeper during their download.
